---
title: "p8105_hw6_yw3438"
author: "Yuning Wang"
date: "11/15/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelr)
library(mgcv)
library(viridis)
library(ggridges)

set.seed(1)
```

## Problem 1

```{r message=FALSE}
birthweight = 
  read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    babysex = factor(recode(babysex, "1" = "male", "2" = "female")),
    frace = factor(recode(frace, "1" = "white", "2" = "black", "3" = "asian",
                   "4" = "puerto rican", "8" = "other", "9" = "unknow")),
    malform = factor(recode(malform, "0" = "absent", "1" = "present")),
    mrace = factor(recode(mrace,  "1" = "white", "2" = "black", "3" = "asian",
                   "4" = "puerto rican", "8" = "other"))
  )
```

The birth weight is an outcome that may depend on 'average number of cigarettes smoked per day during pregnancy' and 'mother's race'. We fit the initial model in the following code.

```{r}
fit = lm(bwt ~ smoken + mrace, data = birthweight)
# read the results of the model
fit %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  mutate(term = str_replace(term, "^mrace", "Race: ")) %>% 
  knitr::kable(digits = 3)
```

The plot of model residuals against fitted values are as followed.

- Residuals against 'mother's race'

```{r}
birthweight %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = mrace, y = resid, fill = mrace)) +
  geom_violin() +
  labs(
    title = "Residuals Against Mother's Race",
    x = "Mother's Race",
    y = "Residuals"
  ) +
  theme_bw() +
  theme(legend.position = "bottom") +
  viridis::scale_fill_viridis(
    name = "Mother's Race",
    discrete = T)
```

- Residuals against 'average number of cigarettes smoked per day during pregnancy'

```{r}
birthweight %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = smoken, y = resid)) +
  geom_point() +
  labs(
    title = "Residuals Against Average Number of Cigarettes",
    x = "Average Number of Cigarettes",
    y = "Residuals"
  ) +
  theme_bw() 
```

The model using length at birth and gestation age as predictors is fitted in the following code.

```{r}
fit_bl_gesage = lm(bwt ~ blength + gaweeks, data = birthweight)
```

The model using head circumference, length, sex and all interactions between these is fitted in the following code.

```{r}
fit_3inter = lm(bwt ~ bhead * blength + bhead * babysex + blength * babysex
                + bhead * blength * babysex, data = birthweight)
```

Compare my model to the two models listed above.

```{r}
cv_df = 
  crossv_mc(birthweight, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) %>% 
  mutate(my_fit        = map(train, ~lm(bwt ~ smoken + mrace, data = .x)),
         bl_gesage_fit = map(train, ~lm(bwt ~ blength + gaweeks, 
                                  data = .x)),
         inter3_fit    = map(train, ~lm(bwt ~ bhead * blength + 
                                          bhead * babysex + 
                                          blength * babysex + 
                                          bhead * blength * babysex, 
                                        data = .x))) %>% 
  mutate(rmse_my_fit = map2_dbl(my_fit, test, ~rmse(model = .x, data = .y)),
         rmse_bl_gesage_fit = map2_dbl(bl_gesage_fit, test, 
                                ~rmse(model = .x, data = .y)),
         rmse_inter3_fit = map2_dbl(inter3_fit, test, 
                                ~rmse(model = .x, data = .y)))
# draw the plot
cv_df %>% 
select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() +
  labs(
    title = "Distribution of RMSE values",
    x = "Model",
    y = "RMSE"
  ) +
  theme_bw() 
```

From the distribution of RMSE values for each model, it can be discovered that the RMSE is smallest at the model using head circumference, length, sex and all interactions between these. As a result, it's better to use the last fitted model.


## Problem 2

```{r}
# read in the data
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

 - Estimates of r-squared

```{r}
# Generate the bootstrap samples
boot_straps = 
  weather_df %>% 
  modelr::bootstrap(n = 5000)

# Look at bootstrap results
bootstrap_rsquared = 
  boot_straps %>% 
   mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  janitor::clean_names() %>% 
  select(r_squared, adj_r_squared)

# draw the distribution of estimate
bootstrap_rsquared %>% 
  ggplot(aes(x = r_squared)) +
  geom_density() +
  labs(
    title = "Distribution of r-squared",
    x = "Value of r-squared",
    y = "Density"
  ) +
  theme_bw()
```









